---
title: "Reproducible Research"
editor: visual
format:
  html:
    toc: true
    toc-depth: 2
    toc-expand: 2
    toc-title: Contents
    toc-location: left
    smooth-scroll: true
title-block-banner: true
execute:
  echo: fenced
  warning: false
  #freeze: true
---

#Research oveiew

Reference:ARIMA Model for Accurate Time Series Stocks Forecasting
Author(s): Shakir Khan1, Hela Alghulaiakh2,
Published by: (IJACSA) International Journal of Advanced Computer Science and Applications,Vol. 11, No. 7, 2020

With the increasing of historical data availability and the need to produce forecasting which includes making decisions regarding investments, in addition to the needs of developing plans and strategies for the future endeavors as well as the difficulty to predict the stock market due to its complicated features, This study applied and compared auto ARIMA (Auto Regressive Integrated Moving Average model). Two customize ARIMA(p,D,q) to get an accurate stock forecasting model by using Netflix stock historical data for five years. Between the three models, ARIMA (1,1,33) showed accurate results in calculating the MAPE and holdout testing, which shows the potential of using the ARIMA model for accurate stock forecasting.
Below we will reproduce the study and analyze it.

# Running Code and Analysis

```{r}
#| label = "setup",
#| include = FALSE
library(xts)
library(lmtest)
library(tidyverse)
library(urca)
getwd()
setwd("/Users/yuqingwu/Desktop/RR\ Study/RR\ Project/Reproduce\ the\ research\ process\ and\ key\ findings\ of\ the\ selected\ papers")
```

Import data from the NFLX database,and plot.

```{r}
#| echo: false
data <- read.csv("NFLX.csv")
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")
data %>% glimpse()
data <- xts(data[, -1],order.by = data$Date,frequency = 12)
Adj.Close <- data$Adj.Close
plot(Adj.Close)
```

Exploring Netflix stocks data from 7th April 2015 to 7th April 2020, showed the non-stationary characteristics of time series as shown in Fig.
```{r}
adf_test <- ur.df(Adj.Close$Adj.Close, type = "none", lags = 0)
summary(adf_test)
```
Use adf test, non-stationary data
```{r，error=TRUE}
par(mfrow = c(2, 1)) 
par(mar = c(3, 4, 2, 1))
acf(Adj.Close$Adj.Close,lag.max = 36, ylim = c(-0.1, 0.1),lwd = 5,col = "dark green",na.action = na.pass)  
pacf(Adj.Close$Adj.Close,lag.max = 36,lwd = 5, col = "dark green",na.action = na.pass)
par(mfrow = c(1, 1)) 
```
first-order difference, adf test again, it is a stationary time series
```{r}
dadj <- na.exclude(diff.xts(Adj.Close$Adj.Close))
adf_test_dadj <- ur.df(dadj, type = "none", lags = 0)
summary(adf_test_dadj)
```

plot acf pacf

```{r}
par(mfrow = c(2, 1)) 
acf(dadj,lag.max = 36, ylim = c(-0.1, 0.1),lwd = 5,col = "dark green",na.action = na.pass)  
pacf(dadj,lag.max = 36,lwd = 5, col = "dark green",na.action = na.pass)
par(mfrow = c(1, 1)) 
```

```{r}
library(forecast)
auto.arima(Adj.Close)
```
Determine the arima model pq, first order difference so d is equal to 1, determine arima(1,2,33) and arima(1,1,33)
Through the auto arima function, it is arima(2, 1, 2)
```{r}
cdata.shortx1 <- Adj.Close$Adj.Close["/20171007", ]
arima212 <- Arima(cdata.shortx1$Adj.Close,order = c(2, 1, 2))
arima212
coeftest(arima212)
summary(arima212)
plot(resid(arima212))
tibble(date = index(cdata.shortx1$Adj.Close),resid = arima212 %>% resid() %>% as.numeric()
) %>%
  ggplot(aes(date, resid)) +
  geom_line(col = "royalblue3") +theme_bw()
```
xxx
```{r}
par(mfrow = c(2, 1)) 
acf(resid(arima212),lag.max = 36,ylim = c(-0.1, 0.1),lwd = 5, col = "dark green",na.action = na.pass)
pacf(resid(arima212),lag.max = 36,lwd = 5, col = "dark green",na.action = na.pass)
par(mfrow = c(1, 1))
Box.test(resid(arima212), type = "Ljung-Box", lag = 4)
```

xxx
```{r}
arima1133 <- Arima(cdata.shortx1$Adj.Close,order = c(1, 1,33))
arima1133
coeftest(arima1133)
summary(arima1133)
plot(resid(arima1133))
tibble(date = index(cdata.shortx1$Adj.Close),resid = arima1133 %>% resid() %>% as.numeric()
) %>%
  ggplot(aes(date, resid)) +
  geom_line(col = "royalblue3") +theme_bw()
```
xx
```{r}
par(mfrow = c(2, 1)) 
acf(resid(arima1133),lag.max = 36,ylim = c(-0.1, 0.1),lwd = 5, col = "dark green",na.action = na.pass)
pacf(resid(arima1133),lag.max = 36,lwd = 5, col = "dark green",na.action = na.pass)
par(mfrow = c(1, 1))
Box.test(resid(arima1133), type = "Ljung-Box", lag = 4)
```
xxx
```{r}
arima1233 <- Arima(cdata.shortx1$Adj.Close,order = c(1, 2,33))
arima1233
coeftest(arima1233)
summary(arima1233)
plot(resid(arima1233))
tibble(date = index(cdata.shortx1$Adj.Close),resid = arima1233 %>% resid() %>% as.numeric()
) %>%
  ggplot(aes(date, resid)) +
  geom_line(col = "royalblue3") +theme_bw()
```
xxx
```{r}
par(mfrow = c(2, 1)) 
acf(resid(arima1233),lag.max = 36,ylim = c(-0.1, 0.1),lwd = 5, col = "dark green",na.action = na.pass)
pacf(resid(arima1233),lag.max = 36,lwd = 5, col = "dark green",na.action = na.pass)
par(mfrow = c(1, 1))
Box.test(resid(arima1233), type = "Ljung-Box", lag = 4)
```
xxx
```{r}
forecasts <- forecast(arima212, h = 627) 
forecasts
forecasts$mean
class(forecasts$mean)
as.numeric(forecasts$mean)
forecasts$lower
forecasts$upper
forecasts_data <- data.frame(f_mean  = as.numeric(forecasts$mean),
                             f_lower = as.numeric(forecasts$lower[, 2]),
                             f_upper = as.numeric(forecasts$upper[, 2]))

forecasts_data 
```

xxx
```{r}
cdata.shortx1 <- Adj.Close$Adj.Close["/20171007", ]
cdata.shortx1
```

xxxx
```{r}
tail(cdata.shortx1)
cdata.shortx2 <-Adj.Close$Adj.Close["20171007/", ]
forecasts_xts <- xts(forecasts_data,order.by =index(cdata.shortx2))
```
xxx
```{r}
cdata3 <- merge(Adj.Close,forecasts_xts)
```

xxx
```{r}
head(cdata3)
tail(cdata3, n =627)
plot(cdata3)
```
xxx
```{r}
forecasts <- forecast(arima1133, h = 627) 
forecasts
forecasts$mean
class(forecasts$mean)
as.numeric(forecasts$mean)
forecasts$lower
forecasts$upper
forecasts_data <- data.frame(f_mean  = as.numeric(forecasts$mean),
                             f_lower = as.numeric(forecasts$lower[, 2]),
                             f_upper = as.numeric(forecasts$upper[, 2]))

forecasts_data 
```
xxx
```{r}
cdata.shortx1 <- Adj.Close$Adj.Close["/20171007", ]
cdata.shortx1
```
xxx
```{r}
tail(cdata.shortx1)
cdata.shortx2 <-Adj.Close$Adj.Close["20171007/", ]
forecasts_xts <- xts(forecasts_data,order.by =index(cdata.shortx2))
```
xxx
```{r}
cdata3 <- merge(Adj.Close,forecasts_xts)
```
xx
```{r}

head(cdata3)
tail(cdata3, n =627)
plot(cdata3)

```
xxx
```{r}
forecasts <- forecast(arima1233, h = 627) 
forecasts
forecasts$mean
class(forecasts$mean)
as.numeric(forecasts$mean)
forecasts$lower
forecasts$upper
forecasts_data <- data.frame(f_mean  = as.numeric(forecasts$mean),
                             f_lower = as.numeric(forecasts$lower[, 2]),
                             f_upper = as.numeric(forecasts$upper[, 2]))

forecasts_data 
```
xxx
```{r}
cdata.shortx1 <- Adj.Close$Adj.Close["/20171007", ]
cdata.shortx1
```
xxx
```{r}
tail(cdata.shortx1)
cdata.shortx2 <-Adj.Close$Adj.Close["20171007/", ]
forecasts_xts <- xts(forecasts_data,order.by =index(cdata.shortx2))
```
xxx
```{r}
cdata3 <- merge(Adj.Close,forecasts_xts)
```
Use the first 50% of the data, use the above three armia models to make predictions, and use the remaining 50% of the data for comparison and plot
```{r}
head(cdata3)
tail(cdata3, n =627)
plot(cdata3)
```
#Summary of the Reproducible Research
We replicated the research process based on the original paper and obtained consistent conclusions. The study analyzed historical data of Netflix stocks from April 7, 2015, to April 7, 2020, to evaluate the performance of the auto ARIMA model and two customized ARIMA (p, D, q) models. After conducting multiple tests, the ARIMA (1, 1, 33) model demonstrated accurate results in calculating values, indicating the potential of using the ARIMA model for precise stock forecasting. This accurate prediction can assist investors in making informed decisions regarding their stock investments. 
